Turbulence in compact to giant HII regions

### 2022-05-13 strucfunc_paper.tex
Javier changes 2022-05-13

Particularly the EON observations, which are the oldest, the fitting procedure gives a noise value of \SI{5.6}{km^{2}.s^{-2}} larger that the \(\sigma^2\pos\) value of \SI{3}{km^{2}.s^{-2}}.
The derived correlation length \(r_0 = \SI{0.05}{pc}\) is \num{6} times smaller
than the box size, which is the minimum value for this ratio of our sample. 
Hence we can confirm that the finite map has no effect in our results.
The derived seeing parameter \(s_0 = \SI{0.002}{pc}\), consistent with the Orion core fit, is more than \num{250} times smaller than \(r_0\).
This large ratio is because the separation of the pixels for the EON observations are at separations above the observational seeing, so these parameter has virtually no effect in our model for the EON case.
The previous statement can be confirmed with the Fig. \ref{fig:corner-Galactic}b which shows the corner plot for the EON.
The RMS seeing posterior is flat, meaning that the values in that range doesn't modify the fit.

>>>>

%Particularly the EON observations, which are the oldest, the fitting procedure gives a noise value of \SI{5.6}{km^{2}.s^{-2}} larger that the \(\sigma^2\pos\) value of \SI{3}{km^{2}.s^{-2}}.
For the EON the derived correlation length \(r_0 = \SI{0.05}{pc}\) is \num{6} times smaller
than the box size, which is the minimum value for this ratio of our sample. 
Hence we can confirm that the finite map has no effect in our results.
The derived seeing parameter \(s_0 = \SI{0.002}{pc}\), consistent with the Orion core fit, is more than \num{250} times smaller than \(r_0\).
This large ratio is because the separation of the pixels for the EON observations are at separations above the observational seeing, so these parameter has virtually no effect in our model for the EON case.
The previous statement can be confirmed with the Fig. \ref{fig:corner-Galactic}b which shows the corner plot for the EON.
The RMS seeing posterior is flat, meaning that the values in that range doesn't modify the fit.
